---
output: 
    pdf_document:
        keep_tex: true
        fig_caption: true
header-includes:
    \usepackage{graphicx}
    \usepackage{geometry}
    \geometry{
        right  = 0.25in,
        left   = 0.25in,
        top    = 0.75in,
        bottom = 0.75in
    }
    \usepackage{fancyhdr}
    \usepackage{lastpage}
    \usepackage{changepage}
    \usepackage[default]{lato}
    \usepackage[none]{hyphenat}
    \usepackage[T1]{fontenc}
    \usepackage{color}
    \usepackage{xcolor}
    \usepackage{enumitem}
    \renewcommand*{\familydefault}{\sfdefault}
    \definecolor{orchardgreen}{HTML}{00945e}
---
\newcommand{\reportcategory}{Home Pricing Golden State}
\newcommand{\reportdate}{Kabbage 18 Month Fixed Term Report}
\newcommand{\frontpagenote}{18 Month Loans Originated prior October 31, 2017}

\fancypagestyle{firstpage}{
    \setlength{\headheight}{35pt}
    \newcommand\headline{\rule[.5cm] {12.4cm}{.4pt}\hfill}
    \newcommand\footline{\hrule height .4pt\hfill}
    \renewcommand\headrule{\vskip-15px\headline\vskip7px\headline}
    \renewcommand\footrule{\footline\vskip10px}
    \renewcommand{\headrulewidth}{3pt}
    \setlength{\marginparwidth}{5pt}
    \fancyfoot{}
    \fancyhead[L]{
        \large 
            {\includegraphics[height = 11px]{/Users/ndelzingaro/Box/static/kabbage_logo.png}}
            {\hspace{10px}\fontsize{9pt}{8pt}\selectfont\fontseries{l} {\color{orchardgreen}{\reportcategory{}}}}
            \\{\vspace{12px}\fontsize{20pt}{16pt}\selectfont\fontseries{l} \fontsize{20pt}{16pt}{\hspace{5px}\selectfont\fontseries{bx} \reportdate{}}} 
            \\{\vspace{10px}\fontsize{7pt}{7pt}\selectfont\fontseries{b} \frontpagenote{}}
    }
 
    \lfoot{\raisebox{16px}{\includegraphics[height = 8px]{/Users/ndelzingaro/Box/static/kabbage_image.png}}}
    \rfoot{\raisebox{15px}{\small{Page \thepage\ of \pageref*{LastPage}}}}
  
}

\fancypagestyle{contentpage}{
    \setlength{\headheight}{20pt}
    \newcommand\hrulethick{\hrule height .8pt\hfill}
    \newcommand\hrulethin{\hrule height .4pt\hfill}
    \renewcommand\headrule{\vskip-16px\hrulethick\vskip20px\hrulethin}
    \renewcommand\footrule{\hrulethin\vskip3px}
    \fancyfoot{}
    \lhead{
        \raisebox{-12px}{\includegraphics[height = 10px]{/Users/ndelzingaro/Box/static/kabbage_logo.png}
        {\hspace{10px}\fontsize{9pt}{8pt}\selectfont\fontseries{l}} {\color{orchardgreen}{\reportcategory{}}}}
    }
    \rhead{\raisebox{-12px}{\reportdate{}}}
    \lfoot{\raisebox{2px}{\includegraphics[height = 8px]{/Users/ndelzingaro/Box/static/kabbage_image.png}}}
    \rfoot{\raisebox{1px}{\small{Page \thepage\ of \pageref*{LastPage}}}}
}

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=10, fig.height=6, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

options(device = function(file, width, height) {
  svg(tempfile(), width = width, height = height)
})
```


```{r setup}
rm(list=ls())

library(tidyquant)
library(tidyverse)
library(lubridate)
library(data.table)
library(ggridges)
library(extrafont)
library(dplyr)
library(ggplot2)
library(hrbrthemes)
#if(!require("animation")) install.packages('animation')
library(devtools)
install_github("yihui/animation")
library(animation)
library(tweenr)


# TODO: These should all move to a separate package
export_theme <- theme_ipsum() +
      theme(text=element_text(family="Lato"),
            panel.background = element_blank(),
            panel.grid.major.x = element_blank(),
            panel.grid.minor = element_blank(),
            panel.grid.major.y = element_line(color='#999999'),
            plot.title = element_text(size=15),
            axis.title = element_text(size=14),
            axis.text = element_text(size=12),
            axis.text.x = element_text(angle = 0, vjust = .5),
            axis.line = element_blank(),
            legend.text=element_text(size=12))

orchard_palette <- c('#006c91', '#222222', '#848484','#990033', '#ff9900', '#660066', '#8b572a', '#e00e7c', '#4fcbe5', '#8a76d4', '#7ed321', '#d7bf1e', '#5891d4', '#d48758', '#e36e74')

format_si <- function(...) {
  function(x) {
    limits <- c(1e-9,  1e-6,  1e-3,  1e0,   1e3,
                1e6,   1e9,   1e12,  1e15,  1e18,
                1e21,  1e24)
    prefix <- c("n",   "µ",   "m",   " ",   "K",
                "MM",   "B",   "T",   "P",   "E",
                "Z",   "Y")
  
    # Vector with array indices according to position in intervals
    i <- findInterval(abs(x), limits)
  
    # Set prefix to " " for very small values < 1e-24
    i <- ifelse(i==0, which(limits == 1e0), i)

    paste(format(round(x/limits[i], 1),
                 trim=TRUE, scientific=FALSE, ...),
          prefix[i], sep = '')
  }
}


format_month <- function(...) {
  function(x) {
    paste(month(x),"'",substr(year(x), 3, 4), sep = '')
  }
}

format_quarter <- function(...) {
  function(x) {
    paste('Q', quarter(x)," ",substr(year(x),3,4), sep = '')
  }
}

get_state_name <- function(x) {
  if(x %in% state.abb) {
    to_return <- tolower(state.name[grep(x, state.abb)])
  } else if (x %in% state.name) {
    to_return <- tolower(x)
  } else if (x == 'DC') {
    to_return <- 'district of columbia'
  } else if (x == 'US') {
    to_return <- 'United States'
  } else {
    to_return <- 'Invalid State Name'
  }
  to_return
}

```

```{r excel_setup}
suppressMessages(  {
  
# Get house price data ----

df.hpi<-fread("https://www.fhfa.gov/DataTools/Downloads/Documents/HPI/HPI_master.csv")

df.hpi <- mutate(df.hpi,date=as.Date(ISOdate(yr,period*3,1)))

df.hpi <- df.hpi %>% group_by(level,place_name) %>% mutate(hpa=index_sa/lag(index_sa)-1,
                                                           hpa4 = index_sa/lag(index_sa,4)-1) %>% ungroup()

# list of CA index
# use grepl("CA",unique(df.hpi$place_name)) to find California

df.ca <- filter(df.hpi,grepl("CA",place_name)| place_name=="California" , hpi_type=="traditional", hpi_flavor=="purchase-only")

df.us <- filter(df.hpi, place_name=="United States", hpi_type=="traditional",hpi_flavor=="purchase-only", frequency=="quarterly")



})
```

\

<!-- CONTENT BEGINS HERE --> 

\thispagestyle{firstpage}

\newpage
\thispagestyle{contentpage}
\fontsize{8pt}{12pt}\selectfont\fontseries{l}

```{r query_securitization_1}
ggplot(data= df.ca %>% filter(level=="State"), aes(x=date,y=index_sa,group=place_name))+
  geom_line(color=rgb(103,180,75, maxColorValue = 256), size=1.05)+
  geom_text(data=. %>% tail(1), aes(label="CA"),color=rgb(103,180,75, maxColorValue = 256),fontface="bold",nudge_y=5)+
  geom_line(data=df.us %>% select(date,index_sa), aes(group="CA"),linetype=2, color=rgb(9, 177,240, maxColorValue = 256),size=1.05)+
  geom_text(data=df.us %>% select(date,index_sa) %>% tail(1), aes(group="CA",label="US"),nudge_y=-5, color=rgb(9, 177,240, maxColorValue = 256))+
  #theme_ridges(font_family="Roboto")+
  theme(text = element_text(color = "#27408b"))+
  labs(y="House Price Index: 1991Q1=100",x="date (quarterly)",
       title="House price index: CA vs US",
       caption="@lenkiefer Source: FHFA purchase-only house price index, SA")
```

```{r loanlevel}
ggplot(data= df.ca %>% filter(level=="State",year(date)>1991), aes(x=date,y=hpa4,group=place_name))+
  geom_line(color=rgb(103,180,75, maxColorValue = 256), size=1.05)+
  geom_text(data=. %>% tail(1), aes(label="CA"),color=rgb(103,180,75, maxColorValue = 256),fontface="bold",nudge_y=.01)+
  geom_line(data=filter(df.us,year(date)>1991) %>% select(date,hpa4), aes(group="CA"),linetype=2, color=rgb(9, 177,240, maxColorValue = 256),size=1.05)+
  geom_text(data=df.us %>% select(date,hpa4) %>% tail(1), aes(group="CA",label="US"),nudge_y=-.01, color=rgb(9, 177,240, maxColorValue = 256))+
  #theme_ridges(font_family="Roboto")+
  scale_y_continuous(labels=scales::percent)+
  theme(text = element_text(color = "#27408b"))+
  labs(y="4-quarter % change",x="date (quarterly)",
       title="House price appreciation: CA vs US",
       subtitle="4-quarter percent change in index",
       caption="@lenkiefer Source: FHFA purchase-only house price index, SA")
```


```{r AccoutLevel}
ggplot(data= df.ca %>% filter(level=="MSA",year(date)>1991), aes(x=date,y=index_sa,group=place_name))+
  geom_line(color=rgb(103,180,75, maxColorValue = 256), size=1.05)+
  geom_line(data=df.ca %>% filter(level=="State",year(date)>1991) %>% select(date,index_sa), aes(group="CA"),linetype=2, color=rgb(9, 177,240, maxColorValue = 256),size=1.05)+
 # theme_ridges(font_family="Roboto")+
  theme(text = element_text(color = "#27408b"),strip.text=element_text(size=7))+
    labs(y="House Price Index: 1991Q1=100",x="date (quarterly)",
       title="House price index", subtitle="Solid line metro, dotted line CA",
       caption="@lenkiefer Source: FHFA purchase-only house price index, SA")+
  facet_wrap(~place_name,ncol=3)
```
\centering

```{r MonthsOffer}
ggplot(data=filter(df.ca,date==max(df.ca$date)), aes(x=forcats::fct_reorder(place_name,hpa4),y=hpa4,color=level))+
  scale_color_manual(name="Level", values=c(rgb(103,180,75, maxColorValue = 256),rgb(9, 177,240, maxColorValue = 256) ))+
  geom_segment(aes(yend=0,xend=place_name))+
  geom_point(size=3)+
  coord_flip()+scale_y_continuous(labels=scales::percent, expand=c(0,0.001),limits=c(0,.175))+
  geom_text(aes(label=scales::percent(round(hpa4,3))), hjust=0,nudge_y=0.0035)+
 # theme_ridges(font_family="Roboto")+
    theme(text = element_text(color = "#27408b"),legend.position="bottom")+
  labs(y="4-quarter % change",x="Area",
       title="House price appreciation: 2018Q1",
       subtitle="4-quarter percent change in index",
       caption="@lenkiefer Source: FHFA purchase-only house price index, SA")
```

```{r MonthsOffer2}


dfp <- filter(df.ca,level=="State",year(date)>1991) %>% select(date,hpa4) %>% mutate(day=1+(row_number()-1)*7, ease="linear", rate_label=as.factor(as.character(round(hpa4,0))))

plot_data_tween<-tween_elements(dfp, time = "day",  group="ease",
                                ease="ease", nframes = nrow(dfp)*2)
df_tween_appear <- tween_appear(plot_data_tween, time='day', nframes = nrow(dfp)*2)


make_plot_appear <- function(i){
  p <-
    ggplot(data=df_tween_appear, aes(x=date,y=hpa4))+
    geom_area(data= .%>% filter(.frame==i, .age> -3.5), color=NA, fill=rgb(9, 177,240, maxColorValue = 256),alpha=0.15 ) +
    geom_line(alpha=0)+
    geom_hline(yintercept=0, linetype=2)+
    geom_line(data= .%>% filter(.frame==i, .age> -3.5) ) +
    geom_point(data=  .%>% filter(.frame==i, .age> -3.5) %>% tail(1), color=rgb(103,180,75, maxColorValue = 256), size=3, alpha=0.5)+
    #theme_ridges(font_family="Roboto")+
        scale_y_continuous(labels=scales::percent, sec.axis=dup_axis())+
    theme(text = element_text(color = "#27408b"))+
    labs(y="House Price Appreciation (y/y %)",x="date (quarterly)",
         title="House price appreciation: California",
         subtitle="4-quarter percent change in index",
         caption="@lenkiefer Source: FHFA purchase-only house price index, SA")
  
  return(p)
}

make_plot_appear(max(df_tween_appear$.frame))
```
&nbsp;

\newpage
\thispagestyle{contentpage}
\fontsize{8pt}{12pt}\selectfont\fontseries{l}

```{r query_originations}
oopt<-ani.options(interval=1/20)
saveGIF({for (i in 1:max(df_tween_appear$.frame)){
  g<-
    make_plot_appear(i) + 
    geom_hline(yintercept=0, linetype=2)
  print(g)
  print(paste(i,"out of",max(df_tween_appear$.frame)))
  ani.pause()
}
  for (ii in 1:2){
    print(g)
    ani.pause()
  }
  
}, movie.name = "~/git_dir/analytics/Macro_Economics_analysis/West_Coast_Home_Pricing/hpa.gif", ani.width=700, ani.height=600,scale=1.2)  #set YOURDIRECTORY to where you want to save the file
```
